A novel distributed nature-inspired algorithm for solving optimization problems

### 2021-09-30 paper.tex
Final Updates
Background relocation
Final Updates
Introduction improvement

We present the description of the following sections in our paper. First, we do
a brief explanation of our motivation for this research in section 2, next, we
present our algorithm inspired by the Life-Cycle of animal species in section
3, followed by our experimental configuration and results in section 4, then we
analyze and describe some of our research findings in section 5, and we
finalize by presenting some inferences based on our experiments' results in
section 6.

\section{Background}

% For citations of references, we prefer the use of square brackets
% and consecutive numbers. Citations using labels or the author/year
% convention are also acceptable. The following bibliography provides
% a sample reference list with entries for journal
% articles~\cite{ref_article1}, an LNCS chapter~\cite{ref_lncs1}, a
% book~\cite{ref_book1}, proceedings without editors~\cite{ref_proc1},
% and a homepage~\cite{ref_url1}. Multiple citations are grouped
% \cite{ref_article1,ref_lncs1,ref_book1},
% \cite{ref_article1,ref_book1,ref_proc1,ref_url1}.
% Multiple citations are grouped \cite{valdez2021container,krejca2020lower,witt2019upper,merelo2016nodio,merelo2016performance,fortin2012deap,stanley2002evolving}.

@@

%
%
%

>>>>

We present the description of the following sections in our paper. First, we
introduce our algorithm inspired by the Life-Cycle of animal species in section
2, followed by our experimental configuration and results in section 3, we
analyze and describe some of our research findings in section 4, and we
finalize by presenting some inferences based on our experiments' results in
section 5.

@@

\section*{Acknowledgments}

This paper has been supported in part by projects DeepBio
(TIN2017--85727--C4--2--P) and TecNM Project 11356.21\@.
%
%
%
